Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-12 eswc-2012/phdsymp.tex
move qtree to sota
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@68 43ef1190-90fd-4dd7-a769-d0121f02b80e
TeXing
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@70 43ef1190-90fd-4dd7-a769-d0121f02b80e
fed approaches
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@71 43ef1190-90fd-4dd7-a769-d0121f02b80e

\documentclass{llncs}
%\documentclass{article}

\begin{document}
\title{Sharing statistics for SPARQL Federation optimization, with
  emphasis on benchmark quality}
\author{Kjetil Kjernsmo}
\institute{Department of Informatics,
Postboks 1080 Blindern,
0316 Oslo, Norway}

\maketitle

\email{kjekje@ifi.uio.no}

@@

A recent scientific treatment of the current specification, is in
\cite{springerlink:10.1007/978-3-642-21064-8_1}. In this paper, the
authors also show an optimization strategy based on execution order of
different algebraic elements. % TODO: wording here

In \cite{5337556}, it is shown how various statistics-gathering
techniques, including histograms can be computed to
assist the SemWIQ optimizer, written by the same authors.

@@

\cite{Harth:2010:DSO:1772690.1772733} introduced QTrees to alleviate
the problem, but it is not clear to me if it will solve it.

@@

There are many possible approaches for this part of the thesis. At
this stage, it seems that use of selectivity estimation may be the
most feasible direction.

@@

>>>>

\documentclass{llncs}
%\documentclass{article}
\usepackage{cite}

\title{Sharing statistics for SPARQL Federation optimization, with
  emphasis on benchmark quality}
\author{Kjetil Kjernsmo}
\institute{Department of Informatics,
Postboks 1080 Blindern,
0316 Oslo, Norway}

\begin{document}

\maketitle
\email{kjekje@ifi.uio.no}

@@

A recent scientific treatment of the current specification, is in
\cite{springerlink:10.1007/978-3-642-21064-8-1}. In this paper, the
authors also show an optimization strategy based on execution order of
different algebraic elements. % TODO: wording here

In \cite{5337556}, it is shown how various statistics-gathering
techniques, including histograms can be computed to assist the SemWIQ
optimizer, written by the same authors.
\cite{Harth:2010:DSO:1772690.1772733} introduced QTrees, which may
alleviate the problem of histogram size, but it may not solve it.

@@

@@

There are many possible approaches for this part of the thesis. As I
expect great advances to be made before I start tackling this problem,
I have not chosen any methodology, but work to find more
space-efficient ways to expose statistics in the service description
and standardize those seems like an interesting direction.

To this end, I briefly looked into two approaches:
\cite{Getoor:2001:SEU:375663.375727} used Bayesian Networks and
Probabilistic Relational Models to efficiently represent the joint
distribution of database tables, a formalism that could be extended to
RDF databases.

Another approach that I have not seen used in the literature is to use
parameterized statistics. This would amount to attempt fitting data to
a known distribution function and expose which distribution and its
parameters in the service description.

Finally, I have seen little work on the problem of rapidly changing
data, so the adaption of existing techniques to such situations may
also be a interesting problem.

@@

\bibliographystyle{plain}
\bibliography{selectivity,federation,benchmarks}
